### 2023-01-17 doc/manuscript/translocation.qmd
Improve text describing evolutionary rescue expectations

-   Differences in allele frequencies between naive and recovering populations

@@

-   Changes in population growth rate extend beyond the natal environment

>>>>

-   Differences in allele frequencies exist between Bd-naive and recovering populations

@@

-   Changes in population growth rate due to evolution extend beyond the natal environment
